Comparing OTU quality across clustering strategies

### 2021-05-11 exploratory/2021/compare-strategies_2021-05.Rmd
Move caption to make plots equal height

```{r otu-quality_cowplot-revised, fig.width = 6, fig.height = 4.5}
plot_quality <- function(dat, y_val, title = '') {
  dat %>% 
    ggplot(aes(strategy, {{ y_val }}, 
               #color = method, 
               shape = method)) + 
    facet_wrap(dataset ~ ., nrow=1) +
    scale_shape_manual(values = list(open = 1, closed = 19)) +
    #scale_color_manual(values = tri_colors) +
    scale_y_continuous(labels = c('0', '0.5', '1'), 
                       breaks = c(0, 0.5, 1),
                       limits = c(0, 1)) +
    coord_flip() +
    labs(x = '', y = '', title = title) +
    theme_bw()
}
mcc_plot <- sum_optifit %>% 
  plot_quality(mcc_median, title = 'Median MCC') +
    geom_hline(data = sum_opticlust, 
               aes(yintercept = mcc_median), 
               linetype = 'dashed', color = 'red') +
    geom_point(size = 3,
               position = position_dodge(width = 0.4))
frac_plot <- sum_optifit %>% filter(method == 'closed') %>% 
  plot_quality(frac_map_median, title = 'Median fraction mapped')  + 
    geom_point(size = 3) +
  labs(caption = "dashed line: _de novo_ clustering") +
  theme(plot.caption = element_markdown(hjust = 0),
        plot.caption.position = 'plot')

@@

main_plot <- plot_grid(mcc_plot + 
    theme(legend.position="none"), frac_plot + 
    theme(legend.position="none"), 
                       ncol = 1, align = 'v', labels = 'AUTO')

>>>>

```{r otu-quality_cowplot-revised, fig.width = 6, fig.height = 4.5}
plot_quality <- function(dat, y_val, title = '') {
  dat %>% 
    ggplot(aes(strategy, {{ y_val }}, 
               #color = method, 
               shape = method)) + 
    facet_wrap(dataset ~ ., nrow=1) +
    scale_shape_manual(values = list(open = 1, closed = 19)) +
    #scale_color_manual(values = tri_colors) +
    scale_y_continuous(labels = c('0', '0.5', '1'), 
                       breaks = c(0, 0.5, 1),
                       limits = c(0, 1)) +
    coord_flip() +
    labs(x = '', y = '', title = title) +
    theme_bw() + 
    theme(legend.position="none")
}

mcc_plot <- sum_optifit %>%
  plot_quality(mcc_median, title = 'Median MCC') +
  geom_hline(data = sum_opticlust, aes(yintercept = mcc_median),
             linetype = 'dashed', color = 'red') +
  geom_point(size = 3, position = position_dodge(width = 0.4))

frac_plot <- sum_optifit %>% filter(method == 'closed') %>% 
  plot_quality(frac_map_median, title = 'Median fraction mapped')  + 
    geom_point(size = 3)

@@

main_plot <- plot_grid(mcc_plot, frac_plot,
                       ncol = 1, align = 'v', labels = 'AUTO'
                       ) +
  labs(caption = "dashed line: _de novo_ clustering") +
  theme(plot.caption = element_markdown(size = rel(0.8)))
